Supplemental Information: Exploiting hydraulic geometry to remotely sense gas exchange velocity via the SWOT satellite

### 2022-01-07 docs/scraps.Rmd
fixed figure themes and some ms drafting

>>>>

To assess the influence of SWOT's implicit measurement error on BIKER performance, we use the error models developed by @durandHowWillRadar2020 and @frassonExploringFactorsControlling2021, which the latter implemented on `r nrow(results_k600_rivs[results_k600_rivs$errFlag == 1,])`/`r nrow(results_k600_rivs[results_k600_rivs$errFlag == 0,])` of the rivers. Error in SWOT measurements will come from both the error tolerances intrinsic in the satellite data product as well as radar layover error and river width error. Layover error is the phenomenon when radar returns from different places arrive at the sensor at the same time, leading to taller landscape features appearing closer to the sensor than shorter landscape features that are the same horizontal distance from the sensor [@durandHowWillRadar2020]. Width errors due to poor water classification are ignored but width errors due to the cross-track distance are included [@frassonExploringFactorsControlling2021]. The cross-track distance, reflective of the amount of the river cross-section that falls within SWOT's swath, controls the size of the pixels **help, I on't understand cross-track distance**. @frassonExploringFactorsControlling2021 tested a suite of measurement error scenarios, however here we test only their 'full uncertainty scenario' that most closely represents the measurement errors that will be implicit in SWOT data. *Should this be more elaborately explained now that these data descriptions are moved to the BIKER section?*

To do this, we start from 'McFLI logic' as used in some SWOT RSQ algorithms, where hydraulic properties vary along cross-sections *i* within the reach but the entire mass of water moving through is conserved and thus only varies with timestep *t* [@gleasonTrackingRiverFlows2017]. McFLI logic is laid out in Figure 4. This model implies that the reach-averaged $k_{600}$, which is ultimately a function of streamflow per equations 5-8 [@wangPhysicallyBasedScaling2021], will only vary temporally as well. Under this conceptual river reach model, BIKER predicts a time-varying, reach-averaged $k_{600_t}$.
